\documentclass[report.tex]{subfiles}
\begin{document}
\section{Meetings} % (fold)
\label{sec:meetings}
The following is a summary of all meetings with my supervisor. Our general
arrangement was to meet every two weeks during the two semesters

\subsection{2nd of November 2015} % (fold)
\label{sub:2nd_of_february_2015}
The first meeting between us after the projects were allocated. This was
primarily spent on Ross teaching me the theory behind non-local boxes, as well
as providing information for the Scope \& Outline Plan document that was to be
submitted the week after.
% subsection 2nd_of_february_2015 (end)

\subsection{16th of November 2015} % (fold)
\label{sub:16th_of_november_2015}
We continued on with the background study of Non-local boxes. I was given the
task of trying to create set-ups of non-local boxes in PRISM, however I did
encounter some issues during this period, during which we communicated over
e-mail attempting to help me crack the problems I was having.
% subsection 16th_of_november_2015 (end)

\subsection{3rd of December 2015} % (fold)
\label{sub:3rd_of_december_2015}
This meeting was going over PRISM and the non-signalling parts of the theory. 
We went over preparations for the Poster Day submissions as well during this
meeting, trying to ensure that I was properly prepared for presenting to Isla,
while also going over the accompanying document submission as well. This
meeting concluded the background study aspect of the meetings.
% subsection 3rd_of_december_2015 (end)

\subsection{18th of January 2016} % (fold)
This meeting primarily went recapping my progress over the Christmas period. My
attempts at creating the language were flawed, so we had to dial back and Ross
gave me a much more simple and focused idea to work with. I was e-mailed a list
of tasks for this as well to give me a push in the right direction.
\label{sub:18th_of_january_2016}

% subsection 18th_of_january_2016 (end)
% section meetings (end)
\end{document}