\documentclass[11pt, a4paper]{article}

\begin{document}
\section{Week 6: 26/10/2015 - 01/11/2015}
Having received the allocations the Friday of the previous week. Initial
contact with supervisor was established, and I started looking into background reading. Work was also put into the Project Scope and Outline Plan submission.

\section{Week 7: 02/11/2015 - 08/11/2015}
First meeting with Ross on the 02/11. This was spent continuing with the
background study and the submission. Back and forth e-mails about the submission
were written, with an extra meeting on Friday the 6th for progress on this
submission. It was also established that meetings would occur every two weeks
from this point forward.

\section{Week 8: 09/11/2015 - 15/11/2015}
There was no meeting this week, and this week was mostly spent focusing on other
classes. I did spend the week learning PRiSM as well, although it was not as
in-depth as I would have liked.

\section{Week 9: 16/11/2015 - 22/11/2015}
Second meeting with Ross on 16/11. We continued with the theory, as well as some
discussion about the next submission. I was given the task of creating models of
non-local boxes in PRiSM, which would be necessary to understand to be able to
create a language and its compiler. Work was done on this, but other classes
prevented serious progress.

\section{Week 10: 23/11/2015 - 29/11/2015}
Project work was primarily focused on creating these models. I spent some time
on background reading to assist with the model creation, but clumsiness on the
Wednesday I was doing this severely hampered progress. Consideration was spent
on the next submission.

\end{document}