\documentclass[report.tex]{subfiles}
\begin{document}

\chapter{Problem Description and Specification} % (fold)
\label{cha:problem_description_and_specification}

% ==============================================================================
% ==============================================================================

\section{Problem Description} % (fold)
\label{sec:problem_description}
Non-local boxes, as described in Chapter \ref{cha:related_work}, can be modelled
using PRISM, allowing for simulations and experiments to be done using the
models. 

However, the language is more low-level and rudimentary than would be ideal.
For someone interested in studying non-local boxes, the PRISM language may be a
hindrance, especially when set-ups with 4 inputs and outputs reaches 200 lines
even when just dealing with binary digits.

The purpose of this project is to create a language for defining the set-ups of
non-local boxes, and to implement a compiler to convert files of this new
language into PRISM models to be used for further experimentation.
% section problem_description (end)

% ==============================================================================

\section{Requirements} % (fold)
\label{sec:requirements}

\subsection{Functional} % (fold)
\label{sub:functional}
The requirements for this project demand the creation of a new language for
describing non-local boxes. It is important that the language's syntax and
semantics are organized and well meaning, allowing for easy understanding of the
language to create new set-ups.

The compiler must take in a source file of this new language, and perform
correct syntax and semantics checking on the given file. The set-up must be
checked to ensure that it is non-signalling before producing an accurate PRISM
file that defines a model of the set-up provided. It is also required that
meaningful warnings and errors are displayed to alert the user to problems
encountered during the attempted compilation.

% subsection functional (end)
\subsection{Non-Functional} % (fold)
\label{sub:non_functional}
In addition to the functional requirements, there some addition non-functional
requirements as well. Documentation should enable someone to create their own
set-ups with ease using the language, while the language should try to not rely
on PRISM knowledge as much as possible.

In addition, the compiler should run in a relatively short time, providing
documentation for the using and any future maintaining of the compiler. In
addition, it would be ideal to provide a full list of issues of an invalid
set-up rather than halting on the first issue encountered.
% subsection non_functional (end)
% section requirements (end)

\section{Development Approach} % (fold)
\label{sec:development_approach}
The approach to this project started with the breaking down into three main
sections.
\begin{enumerate}
    \item Background study of non-local boxes and PRISM, with the aim to be able
    to make the models of boxes manually.
    \item Defining the Q'Grady language.
    \item Designing and implementing the Q'Grady compiler.
\end{enumerate}

The original intent was for this to be a linear progression from one stage to
the other. The first semester period of university saw the primary focus on that
first stage. However, the end point I thought I had reached turned out to not
be completely accurate, which was not discovered until much later on.

The next step would be designing the language itself, outlining the syntax
and semantics of the language before moving onto compiling. I had started with
the bare minimum language instead before starting compiling, with extra features
added to both concurrently.

The development of the compiler again saw original intention for a linear,
incremental cycle. I planned to start with the syntax, then semantics and
finally generation. Again, this changed to a more concurrent approach based on
language features. In hindsight, starting from this angle may have been a
better idea.

Git was used as version control, with a private repository stored on GitHub for
issue tracking.
% section development_approach (end)
% chapter problem_description_and_specification (end)
\newpage
\end{document}