\documentclass[report.tex]{subfiles}
\begin{document}

\chapter{Related Work} % (fold)
\label{cha:related_work}

% ==============================================================================
% ==============================================================================

\section{Non-Local Boxes} % (fold)
\label{sec:non_local_boxes}
The study of non-local boxes was introduced by Sandu Popescu and Daniel
Rohrlich, physicists in 1993 and 1994, as part of their research on quantum
non-locality was inspired by the CHSH inequality by Causer et al.


Consider a device with two ends, held by Alice and Bob. Each provides an
input (\(x\) and \(y)\), and observe the output produced by the box (\(a\) and
\(b)\). Based on some probability distribution \(P(a,b | x,y)\) where \(a, b, x,
y \in {0, 1}\). 

This device will immediately produce an output when given an input, preventing
any communication as a result of a delayed input. These devices are
non-signalling, forbidding faster than light communication and ensuring that
Alice or Bob cannot use their output to determine the other party's input.

\(x \in {0, 1}\) \(y \in {0, 1}\)
\(a \in {0, 1}\) \(b \in {0, 1}\)


\subsection{PR-Box} % (fold)
\label{sub:pr_box}
The PR-box, originally proposed by and named after Popescu-Rorhlich, can be
considered the `Hello World' of non-local boxes. It is the most basic structure,
with two inputs and two outputs, and is the basis for this area of research.

The PR-Box has the following probability distribution:
\[
    P(a, b | x, y) = 
    \begin{cases}
        \frac{1}{2} & \quad a \text{ XOR } B = x \text{ AND } y \\
        0 & \quad \text{otherwise} \\
    \end{cases}
\]

This set-up can alternatively be described using a matrix denoting the 
probabilities, sacrificing the brevity of the above definition with the ability
to more easily look at specific inputs or outputs.

\begin{center}
\begin{tabular}{l | c c c c}
  & 00 & 01 & 10 & 11 \\
  \hline
  00 & \(\frac{1}{2}\) & 0 & 0 & \(\frac{1}{2}\) \\
  01 & \(\frac{1}{2}\) & 0 & 0 & \(\frac{1}{2}\) \\
  10 & \(\frac{1}{2}\) & 0 & 0 & \(\frac{1}{2}\) \\
  11 & 0 & \(\frac{1}{2}\) & \(\frac{1}{2}\) & 0 \\
\end{tabular}
\end{center}
% subsection pr_box (end)

\subsection{Non-Signalling} % (fold)
\label{sub:non_signalling}
As mentioned in Section \ref{sec:non_local_boxes}, an important part of the
non-local box is that it is non-signalling. Non-signalling means that in the
described experiment, Alice can not be made aware of Bob's choice of input or
vice-versa. This requirement imposes restrictions on the probability
distribution, since the probability of an output should depend solely on its
respective input. 

These restrictions allow for a represented of a reduced probability on the
outputs as well, \(P(a | x)\), which is useful information to have when
working with non-local boxes.

The non-signalling restriction can be represented by the given formulae:
\[\sum_{b} P(a, b | x, y) = \sum_{b} P(a, b | x, y') = P(a | x) 
\quad \forall a, x, y, y'\]
\[\sum_{a} P(a, b | x, y) = \sum_{a} P(a, b | x', y) = P(b | y) 
\quad \forall b, y, x, x'\]

An example using the PR-box where \(a = 0, x = 1, y = 0, y' = 1\):

\(\sum_{b} P(0, b | 1, 0) = \sum_{b} P(0, b | 1, 1) = P(0 | 1)\)

\(P(0, 0 | 1, 0) + P(0, 1 | 1, 0) = P(0, 0 | 1, 1) + P(0, 1 | 1, 1) = P(0 | 1)\)

\(0.5 + 0 = 0 + 0.5 = 0.5\)

\(0.5 = 0.5 = 0.5\)


% subsection non_signalling (end)
% section non_local_boxes (end)

% ==============================================================================

\section{PRISM} % (fold)
\label{sec:prism}
PRISM is a probabilistic model checking tool. It allows for
the modelling of systems which exhibit some random nature to them. Examples
include quantum cryptography or wireless networking protocols. Models as such
discrete-time Markov Chains can be created using the PRISM language, and
experiments can be ran using these models.

PRISM can be used for modelling non-local boxes (see here), although it's
weaknesses in doing so are the inspiration for this project.
% section prism (end)
% chapter related_work (end)

\newpage
\end{document}