\documentclass[11pt, a4paper]{article}

\begin{document}
\section{26/10/2015 - 01/11/2015}
Having received the allocations the Friday of the previous week. Initial
contact with supervisor was established, and I started looking into background
reading. Work was also put into the Project Scope and Outline Plan submission.

\section{02/11/2015 - 08/11/2015}
First meeting with Ross on the 02/11. This was spent continuing with the
background study and the submission. Back and forth e-mails about the submission
were written, with an extra meeting on Friday the 6th for progress on this
submission. It was also established that meetings would occur every two weeks
from this point forward.

\section{09/11/2015 - 15/11/2015}
There was no meeting this week, and this week was mostly spent focusing on other
classes. I did spend the week learning PRiSM as well, although it was not as
in-depth as I would have liked.

\section{16/11/2015 - 22/11/2015}
Second meeting with Ross on 16/11. We continued with the theory, as well as some
discussion about the next submission. I was given the task of creating models of
non-local boxes in PRiSM, which would be necessary to understand to be able to
create a language and its compiler. Work was done on this, but other classes
prevented serious progress.

\section{23/11/2015 - 29/11/2015}
Project work was primarily focused on creating these models. I spent some time
on background reading to assist with the model creation, but clumsiness on the
Wednesday I was doing this severely hampered progress. Consideration was spent
on the next submission, structuring and noting down parts for it. The Friday was
another attempt at the model creation, however, there were issues that were ran
into, since it became obvious that I did not have a full understanding on what I
had to do. This led to little progress being done this week aside from what can
only be called administrative stuff related to the project.

\section{30/11/2015 - 06/12/2015}
Work continued on the PRISM learning. It was finally starting to click for me,
thanks to Ross' insight and help. This allowed me to create NLBs in PRISM to be
the basis for the compiler writing, since I now had an idea on the output of the
Q'Grady Compiler.

Substantial work was made on the Specification deadline. Investigation into Java
libraries was done to determine what would be required, with recommendations
from Ross. I had completed the (Non-)functional requirements and development
process part of the document as well.

\section{07/12/2015 - 13/12/2015}
Further work and completion of the Specification was achieved. Revisions were
required for the non-functional requirements of the document, but I was happy
with what I had done. THe main focus was now the poster day. After preparing the
poster, I went on to then preparing what I was going to say as part of my
presentation to Isla, which occurred on the 9th. This was not perfect, although
I think that the document itself would have made up for any holes in the
presentation.

\section{14/12/2015 - 20/12/2015}
My main focus for this week were deadlines for other classes that interfered
with my plans, due to needing to help my group with the completion of these
assignments.

\section{21/12/2015 - 27/12/2015}
Christmas week, so the project was put to the side while dealing with the
holidays.

\section{28/12/2015 - 03/01/2016}
A continuation of the Christmas/New Year's breaking, again resulting in a lack
of meaningful or substantial progress.

\section{04/01/2016 - 10/01/2016}
Due to an alarming situation regarding the Embedded Systems project, all that
could feasibly be achieved during this time was reading for the project.

\section{11/01/2016 - 17/01/2016}
The same as the previous week. I was getting frustrated at this point due to a
lack of focus and I feel that the time management during the Christmas period
was subpar and not sufficient for the demands of the project. The plan that was
submitted for the Specification was off the rails at this point in time.

\section{18/01/2016 - 25/01/2016}
This was not a good week either. While I now have 3 possible syntaxes for the
language, and a structure for the report. It has been difficult to produce the
denotational semantics in a good way, meaning that I am worryingly behind on the
project.

\section{26/01/2016 - 01/02/2016}
After meeting with Ross, a simpler syntax was chosen, and work began on creating
the parser for that syntax. I created the cup and jflex files necessary for the
parsing, and they were added to the project, meaning that I could now parse this
syntax.

\section{02/02/2016 - 08/02/2016}
I implemented the semantic analysis methods for the compiler, which would ensure
that non-signalling and other constraints on the probability distribution were
maintained. I also worked on the first progress report, summarising what has
been achieved.

\section{09/02/2016 - 15/02/2016}
Worked continued on the non-signalling check, which really only works best with
a (2,2,2) set-up. This was completed, as well as methods for extracting P(a|x)
and similar methods required for the file generation part.

\section{16/02/2016 - 22/02/2016}
Work began on the file generation of the prism models to be generated. However,
the first attempt was flawed since my original attempt was not right, meaning
that the efforts were rather useless.

\section{23/02/2016 - 29/02/2016}
The next attempt at file generation, which really should have been done by now.
While this attempt was an improvement, it was still flawed in forcing a certain
order of decision making, meaning that further changes had to be made.

\section{01/03/2016 - 07/02/2016}
The second progress report was submitted, with the little writing I had. I am
still in the process of figuring out the proper .prism models I am to create for
the file generation, since they still aren't quite right.

\end{document}